### 2017-12-07 manuscript.rmd
changed colors in Figure5 pdf

```{r sex, echo=F, message=F, warning=F, include=F}
par(ask=F)

#These are commented out to avoid outputting the figure on every knit (remove comment to generate)

#Simmap SEX
plotTree(ultratree, lwd = 4)
colors = c("black", "red")
names(colors) = c("Dioecious", "Monoecious")
sex_sim %>% plotSimmap(lwd = 4, add = T, colors=colors)
nodelabels(pie=(describe.simmap(sex_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
sex_obj <- densityMap(sex_sim)
sex_obj$cols[1:length(sex_obj$cols)]<-colorRampPalette(colors=c("blue", "orange"), space="Lab")(length(sex_obj$cols))
 pdf("figures_raw/figure_5_raw_sex.pdf")
 plot(sex_obj)
 dev.off()
```

>>>>

```{r sex, echo=F, message=F, warning=F, include=F}
par(ask=F)
#Simmap SEX
plotTree(ultratree, lwd = 4)
colors = c("black", "red")
names(colors) = c("Dioecious", "Monoecious")
sex_sim %>% plotSimmap(lwd = 4, add = T, colors=colors)
nodelabels(pie=(describe.simmap(sex_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
sex_obj <- densityMap(sex_sim)
sex_obj$cols[1:length(sex_obj$cols)]<-colorRampPalette(colors=c("blue", "orange"), space="Lab")(length(sex_obj$cols))
 pdf("figures_raw/figure_5_raw_sex.pdf")
 plot(sex_obj)
 dev.off()
```
